Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-27 salmon/paper/salmon_paper.Rmd
updated Fig 1

seak$value[which(is.na(seak$value))] = 0
pws$value[which(is.na(pws$value))] = 0
kodiak$value[which(is.na(kodiak$value))] = 0

@@

dat$col = as.numeric(as.factor(dat$species))
ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = cbPalette[col]), position = "stack") +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  scale_fill_manual(values = cbPalette) + theme(legend.position="none") + 
  facet_wrap(~region, scale="free_y")

>>>>

seak$value[is.na(seak$value)] = 0
pws$value[is.na(pws$value)] = 0
kodiak$value[is.na(kodiak$value)] = 0

@@

dat$col = as.numeric(as.factor(dat$species))
ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = species), position = "stack") +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  scale_fill_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
    labels =c("Chinook","Sockeye","Coho","Pink","Chum")) + 
  facet_wrap(~region, scale="free_y")
